Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-02-13 transmission.tex
alpha vs incidence increase in backcalc

During November, incidence starts rising, with regional heterogeneity in the timing of when this occurs.
The most explored explanation for this is the emergence of the Alpha variant, which was more transmissible than previous variants and emerged at different times across the country~\autocite{walkerTracking,daviesEstimated,lythgoeLineage}.
A second peak occurs in late December or early January in all regions; this second peak is larger than the first in all regions except the Northern three (North East, North West, and Yorkshire and the Humber).
\begin{figure}
    \includegraphics{transmission/backcalc-regions}
    \caption[Incidence estimated using backcalculation by region]{%
        Incidence proportion for all of England (A) and its component regions.
        Regions are split into broad groupings of three regions each: Northern (B), Midlands (C), and Southern (D).
        Yorkshire and the Humber is labelled as Yorkshire for brevity.
    }
    \label{transmission:fig:backcalc-regions}
\end{figure}

>>>>

During November, incidence starts rising, with regional heterogeneity in the timing of when this occurs (see \cref{transmission:fig:backcalc-regions}).
The most explored explanation for this is the emergence of the Alpha variant, which was more transmissible than previous variants and emerged at different times across the country~\autocite{walkerTracking,daviesEstimated,lythgoeLineage}.
There is weak evidence that when incidence starts increasing is correlated with when the Alpha variant's spread (see \cref{transmission:fig:backcalc-alpha}).
A second peak occurs in late December or early January in all regions; this second peak is larger than the first in all regions except the Northern three (North East, North West, and Yorkshire and the Humber).
\begin{figure}
    \includegraphics{transmission/backcalc-regions}
    \caption[Incidence estimated using backcalculation by region]{%
        Incidence proportion for all of England (A) and its component regions.
        Regions are split into broad groupings of three regions each: Northern (B), Midlands (C), and Southern (D).
        Yorkshire and the Humber is labelled as Yorkshire for brevity.
    }
    \label{transmission:fig:backcalc-regions}
\end{figure}
\begin{figure}
    \includegraphics{transmission/backcalc-alpha}
    \caption[Correlation of the emergence of Alpha and minimum incidence.]{%
        x-axis: time that S-gene target failure, a marker of the Alpha variant, is estimated to start increasing from baseline by region among CIS test results; from \textcite[table S3]{walkerTracking}.
        y-axis: posterior median and 95\% CrI of the date of minimum incidence in November or early December in each region.
        Linear regression line shown.
    }
\end{figure}
